Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2019-01-31 WholePlotTrajectories.Rmd
relecture

In this study, we monitored over 30 years the response of 75 ha of Neotropical forest plots set up on a gradient of disturbance intensity, from 10 to 60% of ecosystem above-ground biomass (AGB) loss. We made use of a large functional traits database encompassing major leaf, stem and life-history traits in order to draw the taxonomic and functional trajectories in terms of richness, evenness, composition and redundancy. Specifically, we elucidateed (i) the community taxonomic and functional recovery and (ii) the ecological processes underlying community post-disturbance trajectories and discussed the validity and the extent of the IDH in the long term for tropical forest, and (iii) examined community recovery time.

@@

Regarding community functional response in contrast, the IDH seemed disproved.
Whenever the disturbance intensity, both community functional richness and evenness increased, with the recruitment of pioneers that were functionally highly different from the species of the pre-disturbance community [@Denslow1980;@Molino2001].
Above the intensity threshold however, for the most intense disturbance, community functional richness and evenness started to decrease after 15 to 20 years. 
The vacated environmental space was then occupied by short-lived species which prevented the establishment of other species. 
The decline of these short-lived pioneers decreased the functional richness and evenness, but we suggest that the establishment of long-lasting pioneers will follow and the taxonomic and functional trajectories will catch up with those observed for intermediate disturbance [@Walker2009].

The IDH then translated into community post-disturbance taxonomic trajectories, with marked differences below and above an intensity threshold. 
It was however not tangible regarding the functional trajectories, because of their decoupling with taxonomic trajectories.

>>>>

In this study, we monitored over 30 years the response of 75 ha of Neotropical forest plots set up on a gradient of disturbance intensity, from 10 to 60% of ecosystem above-ground biomass (AGB) loss. We made use of a large functional traits database encompassing major leaf, stem and life-history traits in order to draw the taxonomic and functional trajectories in terms of richness, evenness, composition and redundancy. Specifically, we elucidateed (i) the community taxonomic and functional recovery and (ii) the ecological processes underlying community post-disturbance trajectories and discussed the validity and the extent of the IDH, and (iii) examined community recovery time.

@@

Regarding community functional trajectories in contrast, there was neither intermediate disturbance intensity nor time to disturbance, which dismissed the IDH.
The functional response according to disturbance intensity did not display the characteristic hump-shaped trajectories.
Whenever the disturbance intensity, both community functional richness and evenness increased with the recruitment of pioneers that were functionally highly different from the species of the pre-disturbance community [@Denslow1980;@Molino2001].
Above the intensity threshold however, for the most intense disturbance, community functional richness and evenness started to decrease after 15 to 20 years. 
The vacated environmental space was then occupied by short-lived species which prevented the establishment of other species. 
The decline of these short-lived pioneers decreased the functional richness and evenness, but we suggest that the establishment of long-lasting pioneers will follow and the taxonomic and functional trajectories will catch up with those observed for intermediate disturbance [@Walker2009].

The IDH then translated into community taxonomic response, with markedly different trajectories below and above an intensity threshold, and with an intermediate time to disturbance when the intensity remained below the threshold. 
It was however not tangible regarding the functional response, with functional trajectories decoupled from taxonmic ones.

### 2019-01-31 WholePlotTrajectories.tex
relecture

In this study, we monitored over 30 years the response of 75 ha of
Neotropical forest plots set up on a gradient of disturbance intensity,
from 10 to 60\% of ecosystem above-ground biomass (AGB) loss. We made
use of a large functional traits database encompassing major leaf, stem
and life-history traits in order to draw the taxonomic and functional
trajectories in terms of richness, evenness, composition and redundancy.
Specifically, we (i) elucidated community taxonomic and functional
recovery and the underlying ecological processes, (ii) clarified the
validity of the IDH in the long term for tropical forest and its
translation into different trajectories in time, and (iii) examined
community recovery time.

@@

Regarding community functional response in contrast, the IDH seemed
disproved. Whenever the disturbance intensity, both community functional
richness and evenness increased, with the recruitment of pioneers that
were functionally highly different from the species of the
pre-disturbance community \citep{Denslow1980, Molino2001}. Above the
intensity threshold however, for the most intense disturbance, community
functional richness and evenness started to decrease after 15 to 20
years. The vacated environmental space was then occupied by short-lived
species which prevented the establishment of other species. The decline
of these short-lived pioneers decreased the functional richness and
evenness, but we suggest that the establishment of long-lasting pioneers
will follow and the taxonomic and functional trajectories will catch up
with those observed for intermediate disturbance \citep{Walker2009}.

The IDH then translated into community post-disturbance taxonomic
trajectories, with marked differences below and above an intensity
threshold. It was however not tangible regarding the functional
trajectories, because of their decoupling with taxonomic trajectories.

>>>>

In this study, we monitored over 30 years the response of 75 ha of
Neotropical forest plots set up on a gradient of disturbance intensity,
from 10 to 60\% of ecosystem above-ground biomass (AGB) loss. We made
use of a large functional traits database encompassing major leaf, stem
and life-history traits in order to draw the taxonomic and functional
trajectories in terms of richness, evenness, composition and redundancy.
Specifically, we elucidateed (i) the community taxonomic and functional
recovery and (ii) the ecological processes underlying community
post-disturbance trajectories and discussed the validity and the extent
of the IDH, and (iii) examined community recovery time.

@@

Regarding community functional trajectories in contrast, there was
neither intermediate disturbance intensity nor time to disturbance,
which dismissed the IDH. The functional response according to
disturbance intensity did not display the characteristic hump-shaped
trajectories. Whenever the disturbance intensity, both community
functional richness and evenness increased with the recruitment of
pioneers that were functionally highly different from the species of the
pre-disturbance community \citep{Denslow1980, Molino2001}. Above the
intensity threshold however, for the most intense disturbance, community
functional richness and evenness started to decrease after 15 to 20
years. The vacated environmental space was then occupied by short-lived
species which prevented the establishment of other species. The decline
of these short-lived pioneers decreased the functional richness and
evenness, but we suggest that the establishment of long-lasting pioneers
will follow and the taxonomic and functional trajectories will catch up
with those observed for intermediate disturbance \citep{Walker2009}.

The IDH then translated into community taxonomic response, with markedly
different trajectories below and above an intensity threshold, and with
an intermediate time to disturbance when the intensity remained below
the threshold. It was however not tangible regarding the functional
response, with functional trajectories decoupled from taxonmic ones.
